Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization.

### 2018-10-28 tex/paper.tex
Supplementary added

The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}. We can see that the optimization computed similar end-result for most regularization parameters. More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$. Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$ .

From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.

@@

In Tab.\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$. This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$. This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.

@@

\begin{table}
\centering
\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$. The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
\hline
 1.0e+00 	 & 1.0e+02 	 & 20 & 600 	 & +6.412 & +0.175 & +0.086 & +0.124 \\
 1.0e+00 	 & 1.0e+02 	 & 40 &  -   & +6.702 & +0.130 & +0.082 & +0.125 \\  
 1.0e+00 	 & 1.0e+00 	 & 20 & 300 	 & +5.538 & +0.324 & +0.148 & +0.128 \\ 
 1.0e+00 	 & 1.0e+00 	 & 40 & 346 	 & +11.392 & +0.873 & +0.242 & +0.154 \\ 
 1.0e+00 	 & 1.0e-02 	 & 20 & 415 	 & +18.156 & +1.378  & +0.389  & +0.251 \\ 
 1.0e+00 	 & 1.0e-02 	 & 40 & 856 	 & +64.050 & +17.408 & +15.950 & +0.614 \\ 
 1.0e+00 	 & 1.0e-04 	 & 20 & 417 	 & +17.747 & +1.465  & +0.406  & +0.258 \\ 
 1.0e+00 	 & 1.0e-04 	 & 40 & 946 	 & +72.594 & +17.985 & +16.702 & +0.641 \\
 1.0e+00 	 & 1.0e-06 	 & 20 & 399 	 & +17.407 & +1.466  & +0.406  & +0.258 \\ 
 1.0e+00 	 & 1.0e-06 	 & 40 & 863 	 & +60.448 & +18.043 & +16.732 & +0.641 \\
 \hline
 1.0e-02 	 & 1.0e+02 	 & 20 & 351 	 & +0.865 & +0.001 & +0.017 & +0.027 \\ 
 1.0e-02 	 & 1.0e+02 	 & 40 & 404 	 & +0.846 & -0.049 & +0.010 & +0.026 \\ 
 1.0e-02 	 & 1.0e+00 	 & 20 & 254 	 & +0.018 & +0.007 & +0.008 & +0.007 \\ 
 1.0e-02 	 & 1.0e+00 	 & 40 & 218 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
 1.0e-02 	 & 1.0e-02 	 & 20 & 381 	 & +0.127 & +0.057 & -0.001 & +0.016 \\ 
 1.0e-02 	 & 1.0e-02 	 & 40 & 543 	 & +0.099 & +0.087 & +0.002 & +0.023 \\
 1.0e-02 	 & 1.0e-04 	 & 20 & 641 	 & +0.171 & +0.082 & -0.003 & +0.091 \\ 
 1.0e-02 	 & 1.0e-04 	 & 40 & 879 	 & +0.303 & +0.383 & +0.079 & +0.222 \\ 
 1.0e-02 	 & 1.0e-06 	 & 20 & 547 	 & +0.173 & +0.084 & -0.003 & +0.092 \\
 1.0e-02 	 & 1.0e-06 	 & 40 & 844 	 & +0.332 & +0.416 & +0.095 & +0.239 \\ 
 \hline 
 1.0e-04 	 & 1.0e+02 	 & 20 & 257 	 & +0.853 & -0.001 & +0.017 & +0.026 \\ 
 1.0e-04 	 & 1.0e+02 	 & 40 & 532 	 & +0.822 & -0.051 & +0.010 & +0.026 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 164 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 203 	 & +0.005 & -0.012 & +0.001 & +0.003 \\  
 1.0e-04 	 & 1.0e-02 	 & 20 & 313 	 & +0.071 & +0.021 & -0.001 & +0.007 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 294 	 & +0.004 & +0.004 & -0.001 & +0.001 \\ 
 1.0e-04 	 & 1.0e-04 	 & 20 & 265 	 & +0.108 & +0.035 & -0.002 & +0.014 \\
 1.0e-04 	 & 1.0e-04 	 & 40 & 401 	 & -0.010 & -0.002 & -0.002 & +0.004 \\ 
 1.0e-04 	 & 1.0e-06 	 & 20 & 452 	 & +0.066 & +0.021 & -0.003 & +0.031 \\ 
 1.0e-04 	 & 1.0e-06 	 & 40 & 330 	 & -0.014 & -0.013 & -0.003 & +0.004 \\ 
 \hline
 1.0e-06 	 & 1.0e+02 	 & 20 & 274 	 & +0.850 & -0.001 & +0.017 & +0.026 \\ 
 1.0e-06 	 & 1.0e+02 	 & 40 & 496 	 & +0.821 & -0.051 & +0.010 & +0.026 \\
 1.0e-06 	 & 1.0e+00 	 & 20 & 176 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 207 	 & +0.006 & -0.012 & +0.001 & +0.003 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 223 	 & +0.075 & +0.024 & -0.001 & +0.007 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 392 	 & +0.000 & -0.001 & -0.001 & +0.002 \\ 
 1.0e-06 	 & 1.0e-04 	 & 20 & 429 	 & +0.085 & +0.027 & -0.002 & +0.025 \\ 
 1.0e-06 	 & 1.0e-04 	 & 40 & 241 	 & -0.020 & -0.030 & -0.005 & +0.005 \\ 
 1.0e-06 	 & 1.0e-06 	 & 20 & 591 	 & +0.060 & +0.021 & -0.003 & +0.048 \\ 
 1.0e-06 	 & 1.0e-06 	 & 40 & 343 	 & -0.014 & -0.010 & -0.003 & +0.004 \\

@@

\end{tabular}
\label{Tab::Noise0.03}
\end{table} 
\begin{table}[t]
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
\hline
 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\

>>>>

The results are shown in Table~\ref{Tab::1} and the convergence is shown in Figure~\ref{convergence}. We can see that the optimization computed similar end-result for most regularization parameters. More specifically, for $\alpha \leq 1\mathrm{e}{-2}$ and $\beta \leq 1e-0$ the relative errors for all optimization parameters are below $5\%$.However, in the case of $ \alpha=1.0$ the relative error is over 100\% higher then for other values of $\alpha$. Furthermore, for all $\beta=100.0$ there is about 70\% relative error for $D_{\Omega_1}$ and approximate 10\% error for $D_{\Omega_2}$. From the results it can be discerned that $\alpha =1.0$ and $\beta=100.0$ represent an upper threshold where the observations are no longer the dominant term in the objective functional.

@@

In Table~\ref{Tab::Real-data}, it was shown that the grey matter diffusion coefficient had a negative correlation with the relaxation parameter $\beta$. This was caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering that the grey matter volume has an average thickness less than 3 mm makes it susceptible to changes in $g$. This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.

@@

\begin{table}[t]
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.3, and $t_i =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1}\sp{rel}$ & $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $ & $|| g ||\sp{rel} $ \\
\hline
 1.0e-02 	 & 1.0e+00 	 & 10 & 144 	 & +0.012 & +0.055 & +0.027 & +0.036 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 476 	 & -0.009 & +0.049 & +0.035 & +0.051 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 476 	 & -0.097 & +0.042 & +0.054 & +0.054 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 558 	 & -0.071 & +0.047 & +0.039 & +0.054 \\ 
 1.0e-04 	 & 1.0e+00 	 & 10 & 182 	 & -0.040 & +0.033 & +0.051 & +0.037 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 471 	 & +0.021 & +0.038 & +0.036 & +0.056 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 792 	 & -0.058 & +0.042 & +0.031 & +0.565 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 &  -   & -0.050 & +0.029 & +0.040 & +1.062 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 178 	 & +0.012 & +0.033 & +0.021 & +0.036 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 537 	 & -0.018 & +0.040 & +0.025 & +0.057 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 &  -	 & -0.038 & +0.040 & +0.030 & +1.452 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 &  - 	 & +0.003 & +0.035 & +0.046 & +3.621 \\ 
 1.0e-02 	 & 1.0e+00 	 & 20 & 213 	 & +0.009 & +0.015 & +0.009 & +0.016 \\ 
 1.0e-02 	 & 1.0e-02 	 & 20 & 719 	 & +0.228 & +0.088 & -0.032 & +0.085 \\ 
 1.0e-02 	 & 1.0e-04 	 & 20 &  -   & +0.100 & +0.071 & -0.013 & +0.271 \\ 
 1.0e-02 	 & 1.0e-06 	 & 20 &   -  & +0.223 & +0.097 & -0.027 & +0.282 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 245 	 & +0.038 & +0.013 & -0.001 & +0.016 \\ 
 1.0e-04 	 & 1.0e-02 	 & 20 &  - 	 & +0.050 & +0.054 & -0.024 & +0.116 \\ 
 1.0e-04 	 & 1.0e-04 	 & 20 &  - 	 & -0.087 & +0.059 & -0.077 & +5.763 \\ 
 1.0e-04 	 & 1.0e-06 	 & 20 &  -	 & +0.001 & +0.083 & -0.038 & +7.485 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 242 	 & -0.009 & +0.008 & +0.015 & +0.016 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 947 	 & +0.122 & +0.093 & -0.040 & +0.115 \\ 
 1.0e-06 	 & 1.0e-04 	 & 20 &  - 	 & -0.076 & +0.041 & -0.020 & +7.700 \\ 
 1.0e-06 	 & 1.0e-06 	 & 20 &  - 	 & +0.147 & +0.113 & -0.023 & +10.936 \\

\section{Supplementary}
\begin{table}
\centering
\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$. The observations times were chosen $ t_i=[2.4, 4.8,$ 7.2, 9.6, 12.0, 14.4, $16.8, 19.2, 21.6, 24.0]$ }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel} $ \\
\hline
 1.0e+00 	 & 1.0e+02 	 & 20 & 600 	 & +6.412 & +0.175 & +0.086 & +0.124 \\
 1.0e+00 	 & 1.0e+02 	 & 40 &  -   & +6.702 & +0.130 & +0.082 & +0.125 \\  
 1.0e+00 	 & 1.0e+00 	 & 20 & 300 	 & +5.538 & +0.324 & +0.148 & +0.128 \\ 
 1.0e+00 	 & 1.0e+00 	 & 40 & 346 	 & +11.392 & +0.873 & +0.242 & +0.154 \\ 
 1.0e+00 	 & 1.0e-02 	 & 20 & 415 	 & +18.156 & +1.378  & +0.389  & +0.251 \\ 
 1.0e+00 	 & 1.0e-02 	 & 40 & 856 	 & +64.050 & +17.408 & +15.950 & +0.614 \\ 
 1.0e+00 	 & 1.0e-04 	 & 20 & 417 	 & +17.747 & +1.465  & +0.406  & +0.258 \\ 
 1.0e+00 	 & 1.0e-04 	 & 40 & 946 	 & +72.594 & +17.985 & +16.702 & +0.641 \\
 1.0e+00 	 & 1.0e-06 	 & 20 & 399 	 & +17.407 & +1.466  & +0.406  & +0.258 \\ 
 1.0e+00 	 & 1.0e-06 	 & 40 & 863 	 & +60.448 & +18.043 & +16.732 & +0.641 \\
 \hline
 1.0e-02 	 & 1.0e+02 	 & 20 & 351 	 & +0.865 & +0.001 & +0.017 & +0.027 \\ 
 1.0e-02 	 & 1.0e+02 	 & 40 & 404 	 & +0.846 & -0.049 & +0.010 & +0.026 \\ 
 1.0e-02 	 & 1.0e+00 	 & 20 & 254 	 & +0.018 & +0.007 & +0.008 & +0.007 \\ 
 1.0e-02 	 & 1.0e+00 	 & 40 & 218 	 & +0.020 & -0.006 & +0.001 & +0.003 \\ 
 1.0e-02 	 & 1.0e-02 	 & 20 & 381 	 & +0.127 & +0.057 & -0.001 & +0.016 \\ 
 1.0e-02 	 & 1.0e-02 	 & 40 & 543 	 & +0.099 & +0.087 & +0.002 & +0.023 \\
 1.0e-02 	 & 1.0e-04 	 & 20 & 641 	 & +0.171 & +0.082 & -0.003 & +0.091 \\ 
 1.0e-02 	 & 1.0e-04 	 & 40 & 879 	 & +0.303 & +0.383 & +0.079 & +0.222 \\ 
 1.0e-02 	 & 1.0e-06 	 & 20 & 547 	 & +0.173 & +0.084 & -0.003 & +0.092 \\
 1.0e-02 	 & 1.0e-06 	 & 40 & 844 	 & +0.332 & +0.416 & +0.095 & +0.239 \\ 
 \hline 
 1.0e-04 	 & 1.0e+02 	 & 20 & 257 	 & +0.853 & -0.001 & +0.017 & +0.026 \\ 
 1.0e-04 	 & 1.0e+02 	 & 40 & 532 	 & +0.822 & -0.051 & +0.010 & +0.026 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 164 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 203 	 & +0.005 & -0.012 & +0.001 & +0.003 \\  
 1.0e-04 	 & 1.0e-02 	 & 20 & 313 	 & +0.071 & +0.021 & -0.001 & +0.007 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 294 	 & +0.004 & +0.004 & -0.001 & +0.001 \\ 
 1.0e-04 	 & 1.0e-04 	 & 20 & 265 	 & +0.108 & +0.035 & -0.002 & +0.014 \\
 1.0e-04 	 & 1.0e-04 	 & 40 & 401 	 & -0.010 & -0.002 & -0.002 & +0.004 \\ 
 1.0e-04 	 & 1.0e-06 	 & 20 & 452 	 & +0.066 & +0.021 & -0.003 & +0.031 \\ 
 1.0e-04 	 & 1.0e-06 	 & 40 & 330 	 & -0.014 & -0.013 & -0.003 & +0.004 \\ 
 \hline
 1.0e-06 	 & 1.0e+02 	 & 20 & 274 	 & +0.850 & -0.001 & +0.017 & +0.026 \\ 
 1.0e-06 	 & 1.0e+02 	 & 40 & 496 	 & +0.821 & -0.051 & +0.010 & +0.026 \\
 1.0e-06 	 & 1.0e+00 	 & 20 & 176 	 & +0.008 & +0.003 & +0.008 & +0.007 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 207 	 & +0.006 & -0.012 & +0.001 & +0.003 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 223 	 & +0.075 & +0.024 & -0.001 & +0.007 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 392 	 & +0.000 & -0.001 & -0.001 & +0.002 \\ 
 1.0e-06 	 & 1.0e-04 	 & 20 & 429 	 & +0.085 & +0.027 & -0.002 & +0.025 \\ 
 1.0e-06 	 & 1.0e-04 	 & 40 & 241 	 & -0.020 & -0.030 & -0.005 & +0.005 \\ 
 1.0e-06 	 & 1.0e-06 	 & 20 & 591 	 & +0.060 & +0.021 & -0.003 & +0.048 \\ 
 1.0e-06 	 & 1.0e-06 	 & 40 & 343 	 & -0.014 & -0.010 & -0.003 & +0.004 \\

@@

\end{tabular}
\label{Tab::Noise0.03}
\end{table}
